Software Citation Principles

### 2016-08-21 sc-principles/rebuttal-2/rebuttal.tex

\item{``Software teams can be large and multidisciplinary, \ldots'': I think
this applies to data too.}

\item{``The lifetime of software is generally not as long as that of data.'':
Again unsupported, and again I can imagine this to be false. Many datasets, in
particular small ones, might be stillbirths (i.e.\ they are never used). The
same might be true for software, but possibly to a lesser degree. And software
might commonly evolve, whereas data might more often be replaced by a
different and newer dataset, in which case evolving software would live
longer.}

\end{itemize}

\textbf{Our response:} We, and the overall working group, believe there are significant difference
between software and data, and that these lead to differences in the corresponding citation principles
as well as their application.
However, we agree that there has not been sufficient discussion to document these
differences in a concise, well-structured, and referenced manner.
For this reason, we have removed the list of differences in the paper and point
to an ongoing discussion where a large set of community members are working
to complete this structured documentation with evidence of each point.  An example
of one difference is that appropriate licenses for software are different than appropriate
licenses for data (i.e., for open software, an OSI-approved license, while for open data, a CC license).

### 2016-08-21 sc-principles/software-citation-principles.tex
minor wording edit, and in -> is, for software vs data

We made the adaptations because software, while similar to data in terms of not traditionally having been cited in publications, is also different than data. In the context of research (e.g., in science), the term ``data'' usually refers to electronic records of observations made in the course of a research study (``raw data'') or to information derived from such observations by some form of processing (``processed data''), as well as the output of simulation or modeling software (``simulated data''). 
Some confusion about the distinction between software and data comes in part from the much wider sense that the term ``data'' has in computing and information science, where it refers to anything that can be processed by a computer. In that sense, software is just a special kind of data.
Because of this, citing software is not the same as citing data.  A more general discussion about these distinctions in currently underway~\cite{software-vs-data}.

>>>>

We made the adaptations because software, while similar to data in terms of not
traditionally having been cited in publications, is also different than data.
In the context of research (e.g., in science), the term ``data'' usually refers
to electronic records of observations made in the course of a research study
(``raw data'') or to information derived from such observations by some form
of processing (``processed data''), as well as the output of simulation or
modeling software (``simulated data'').
Some confusion about the distinction between software and data comes in part
from the much wider scope of the term ``data'' in computing and
information science, where it refers to anything that can be processed by a
computer. In that sense, software is just a special kind of data.
Because of this, citing software is not the same as citing data. A more general
discussion about these distinctions is currently
underway~\cite{software-vs-data}.
